---
title: "HW_11"
author: "Amy Hessl"
date: "11/8/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}
library(kableExtra)
library(dplyr)
```

#### apply
data(Titanic) will return a 4-d array resulting from the cross-tabulation of 2201 observations on 4 variables.  The data were originally collected by the British Board of Trade in their investigations related to the sinking of the Titanic.

**1) Using the R data Titanic, use apply to answer the following:**  
```{r}
data("Titanic")
MWSurvived <- as.data.frame(apply(Titanic, c(2, 4), sum))
MWSurvivalRate <- MWSurvived$Yes/(MWSurvived$No+MWSurvived$Yes) #calculate survival rate
MWSurvivalLabeled <- cbind(MWSurvived, MWSurvivalRate) #add rate to table
#Rate of survival is greater for women
MWSurvivalLabeled
```
The rate of survival is greater for women.

```{r}
CASurvived <- as.data.frame(apply(Titanic, c(3, 4), sum)) 
CASurvivalRate <- CASurvived$Yes/(CASurvived$No+CASurvived$Yes) #calculate survival rate
CASurvivalLabeled <- cbind(CASurvived, CASurvivalRate) #add rate to table
#Rate of survival is greater for children
CASurvivalLabeled
```
The rate of survival is greater for children.

#### lapply
**2) Some insect species can only survive if daily temperatures stay above some temperature.  Write a function that takes two arguments, a data frame and a temperature that returns a TRUE when the tmin > X and a FALSE when tmin is < X, where X is the threshold temperature.  Have the function then add a logical vector to each daily climate data frame reporting whether that threshold was exceeded (TRUE) or not (FALSE). Apply this function across all three of the daily data frames provided in /data. For each data frame, your results might look like:**

```{r}
prismDat <- function(path){
  data.path <- path
  glob.path <- paste0(data.path, "*", ".csv")  
  dataFiles <- lapply(Sys.glob(glob.path), read.csv, skip=11, head=F)
  climvars <- c("pdate", "ppt", "tmin", "tmean", "tmax")
  dataFiles <- lapply(dataFiles, setNames, climvars)
  return(dataFiles)
}
```

```{r}
minTemp <- function(df, threshTemp) {
  for (i in 1:nrow (df)){
   if(df$tmin[i] < threshTemp){
      newVector <- FALSE
    }else{
      newVector <- TRUE
    }
  newtable <- cbind(df, newVector)
  return(newtable)
  }
}
```




*Hints:*  

+ Read in the prism daily data files in /data using your prismDat function you made in class.    
+ Write a function that works for a single data frame from the list.  
+ Write an apply function to 'apply' your function across all the data frames in the list.  

