---
title: "HW_11"
author: "Shaun Donmoyer and Sara Schreder-Gomes"
date: "11/21/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}
library(kableExtra)
library(dplyr)
```



**1) Using the R data Titanic, use apply to answer the following:**  
```{r}
data("Titanic")
MWSurvived <- as.data.frame(apply(Titanic, c(2, 4), sum))
MWSurvivalRate <- MWSurvived$Yes/(MWSurvived$No+MWSurvived$Yes) #calculate survival rate
MWSurvivalLabeled <- cbind(MWSurvived, MWSurvivalRate) #add rate to table
#Rate of survival is greater for women
MWSurvivalLabeled
```
The rate of survival is greater for women.

```{r}
CASurvived <- as.data.frame(apply(Titanic, c(3, 4), sum)) 
CASurvivalRate <- CASurvived$Yes/(CASurvived$No+CASurvived$Yes) #calculate survival rate
CASurvivalLabeled <- cbind(CASurvived, CASurvivalRate) #add rate to table
#Rate of survival is greater for children
CASurvivalLabeled
```
The rate of survival is greater for children.

#### lapply
**2) Some insect species can only survive if daily temperatures stay above some temperature.  Write a function that takes two arguments, a data frame and a temperature that returns a TRUE when the tmin > X and a FALSE when tmin is < X, where X is the threshold temperature.  Have the function then add a logical vector to each daily climate data frame reporting whether that threshold was exceeded (TRUE) or not (FALSE). Apply this function across all three of the daily data frames provided in /data. For each data frame, your results might look like:**

```{r}
prismDat <- function(path){
  data.path <- path
  glob.path <- paste0(data.path, "*", ".csv")  
  dataFiles <- lapply(Sys.glob(glob.path), read.csv, skip=11, head=F)
  climvars <- c("pdate", "ppt", "tmin", "tmean", "tmax")
  dataFiles <- lapply(dataFiles, setNames, climvars)
  return(dataFiles)
}
```

```{r}
minTemp <- function(df, threshTemp) {
  for (i in 1:nrow (df)){
   if(df$tmin[i] < threshTemp){
      newVector <- as.logical(FALSE)
    }else{
      newVector <- as.logical(TRUE)
    }
  newtable <- cbind(df, newVector)
  return(newtable)
  }
}
```

``{r}
dataList <- c(myData[[1]], myData[[2]], myData[[3]])
lapply(dataList, minTemp, 3)
```


*Hints:*  
+ Read in the prism daily data files in /data using your prismDat function you made in class.    
+ Write a function that works for a single data frame from the list.  
+ Write an apply function to 'apply' your function across all the data frames in the list.  

#3
+ Request a token from rnoaa. Make a .Rprofile text file (no extension) containing:  
```options(noaakey="your_noaa_token")``` 
and store it at the top of your project directory.    
+ stationid='GHCND:ASN00091245'  
+ Not all years have data!   

```{r}
install.packages('rnoaa') 
```

```{r}
library(rnoaa)
```

```{r}
options(noaakey="vOhMgIvwqWkcgBBlpYPfHSldYhQiTfbR")
```

```{r}
ncdc(datasetid='GSOM', stationid = 'GHCND:ASN00091245', datatypeid='TAVG', startdate = '1991-01-01', enddate = '1991-12-31', limit = 1000, add_units=TRUE)
```



```{r}
library(rnoaa)

options(noaakey="vOhMgIvwqWkcgBBlpYPfHSldYhQiTfbR")

my_df <- data.frame()

for ( i in seq(1985,2019)){ 
  my.query<-ncdc(datasetid='GSOM', stationid ='GHCND:ASN00091245', datatypeid = 'TAVG', startdate = paste0(i, "-01-01"), enddate = paste0(i, "-12-31"), add_units = TRUE)$data
  
  my_df <- rbind(my_df, my.query)
  
}

```



**4) Calculate the average annual temperature and the number of months used to generate that mean from #3 above (years without data can be excluded).  Report in a table, for example:**




```{r}
library(dplyr)

my_df$date <- substr(my_df$date, 1,4) #Gets rid of the time stamp on the date

count_my_df <- my_df %>% # This pipe groups by date, and counts how many times 
  group_by(date) %>%     # each date (year) appears
  tally()

```


```{r}
the_sum <- my_df %>% # This pipe again groups the data by date and then
  group_by(date) %>% # averages the temp vaules for the grouped dates
   summarize(Tavg = mean(value))

```


```{r}
new_data <- cbind(count_my_df, the_sum) ## Combines temp data with year data
final_table <- new_data[,-1] ## Date column appears twice, so I removed one
names(final_table)[names(final_table) == "n"] <- "Months" # Change column name
names(final_table)[names(final_table) == "date"] <- "Year"
final_table %>%
  kable(digits=3) %>%
  kable_styling()
```